** different horizontal spaces
.
Negative thin space: -\negthinspace- \\
Thin space: -\,- \\
Thin space: -\thinspace- \\
Normal space: - - \\
Normal space: -\ - \\
Non-break space: -~- \\
en-space: -\enspace- \\
em-space: -\quad- \\
2x em-space: -\qquad-\\
3cm horizontal space: -\hspace{3cm}- \\
%relative fills: -\hspace{\stretch{1}}-\hspace{\stretch{2}}- % not possible in html!
.
<div class="body">
<p>Negative thin space: ‐<span class="negthinspace"></span>‐<br>
Thin space: ‐ ‐<br>
Thin space: ‐ ‐<br>
Normal space: ‐ ‐<br>
Normal space: ‐​ ‐<br>
Non‐break space: ‐&nbsp;‐<br>
en‐space: ‐ ‐<br>
em‐space: ‐ ‐<br>
2x em‐space: ‐  ‐<br>
3cm horizontal space: ‐<span style="margin-right:113.386px"></span>‐<br>
</p>
</div>
.


** linebreaks with vertical space
.
This is just some simple text.\\[1cm]
This is just some simple text.
.
<div class="body">
<p>This is just some simple text.<span class="breakspace" style="margin-bottom:37.795px"></span>
This is just some simple text.</p>
</div>
.


** \smallskip etc. and \smallbreak etc.: paragraph breaks with vertical space
.
This is just a line of text \smallskip with an embedded small skip.

This is just some simple text.

\medskip
A line after the medskip.

\bigskip

A line after the bigskip.

This is just some simple text.
\smallbreak
A line after the smallbreak with just some simple text.
\medbreak
A line after the medbreak with just some simple text.
\bigbreak
Final line of just some simple text.
.
<div class="body">
<p>This is just a line of text <span class="vspace-inline smallskip"></span>with an embedded small skip.</p>
<p>This is just some simple text.</p>
<span class="vspace medskip"></span>
<p>A line after the medskip.</p>
<span class="vspace bigskip"></span>
<p>A line after the bigskip.</p>
<p>This is just some simple text.</p>
<span class="vspace smallskip"></span>
<p>A line after the smallbreak with just some simple text.</p>
<span class="vspace medskip"></span>
<p>A line after the medbreak with just some simple text.</p>
<span class="vspace bigskip"></span>
<p>Final line of just some simple text.</p>
</div>
.


** \vspace{} in horizontal and vertical mode
.
This is some text, it includes\vspace{1cm} a vertical space. And some more text.

\vspace{1cm}
And another paragraph.
.
<div class="body">
<p>This is some text, it includes<span class="vspace-inline" style="margin-bottom:37.795px"></span> a vertical space. And some more text.</p>
<span class="vspace" style="margin-bottom:37.795px"></span>
<p>And another paragraph.</p>
</div>
.
